---
title: "censurbias"
author: "Enrique Barrajon"
date: '2022-06-14'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
parent_directory <- dirname(getwd())
knitr::opts_knit$set(root.dir = parent_directory) # set the working directory to the parent directory
```

## R Markdown

Once installed these packages, we may use them to update the package

```{r}
# rm(list = ls())
library("devtools")
library("roxygen2")
```

## Load survival with the basic datasets

```{r}

library("survival")
formula1 <- Surv(time, status == 1) ~ x
survfit1 <- survfit(formula1, data = leukemia)
# plot(survfit1)

```

We check the parent directory

```{r}

# setwd(paste(head(strsplit(getwd(), "/")[[1]], -1), collapse = "/"))
getwd()

```

## Update package

Save files and build the help files with reoxygenise.

```{r}

roxygenise()

```

Check documentation

```{r}
# load_all(".")
?CBI
help("CBI")
```


```{r}

CBI(leukemia) # 0.006033516
# CBI(survival::ovarian)
CBI(survival::ovarian, time = "futime", status = "fustat") # 0
CBI(survival::lung, event = 2) # 0.02949085
CBI(survival::veteran)         # 0.5019982
EBI(leukemia) # 0.006033516
# EBI(survival::ovarian)
EBI(survival::ovarian, time = "futime", status = "fustat") # 0
EBI(survival::lung, event = 2) # 0.02949085
EBI(survival::veteran)         # 0.5019982

```

# GitHub repository (https://github.com/Enrique-Barrajon/censurbias_pkg)

Push repository censurbias_pkg from GitKraken app to gitHub with the pull and push url:

https://github.com/Enrique-Barrajon/censurbias_pkg.git

Now, unload the package functions

```{r}

detach(package:censurbias, unload=TRUE)

```

and load from GitHub

```{r}

install_github("Enrique-Barrajon/censurbias")
library(censurbias)
CBI(leukemia)

```


